Finding Code Clone Refactoring Techniques by Mapping Clone Context

### 2021-11-20 cefp/paper.tex
Updates from Overleaf

This is shown schematically in Figure~\ref{fig:clonecontext}.

\todo{Redo figure to show the clone context as a composite of relation, location and contents}
\begin{figure}[H]
  \centering
    \includegraphics[width=0.8\columnwidth]{img/context}
    \caption{Abstract representation of clone classes and clone instances.}
  \label{fig:clonecontext}
\end{figure}

@@

\begin{figure}[H]
  \centering
    \includegraphics[width=0.6\columnwidth]{img/Relation}
      \caption{Abstract figure displaying some relations of clone classes. Arrows represent superclass relations.}
  \label{fig:clonerelation}
\end{figure}

@@

\section{CloneRefactor}
\todo[inline]{add text from other paper}

\section{Experimental Setup}
To find out in which location, relation and contents category most clones are found, we performed measurements on a large corpus of diverse open-source projects. We use the tool CloneRefactor\footnote{CloneRefactor is a code clone detection and refactoring tool: \url{https://github.com/SimonBaars/CloneRefactor}} which automatically determines these context aspects of code clones.

>>>>

@@

\begin{figure}
  \centering
    \includegraphics[width=0.6\columnwidth]{img/Relation}
      \caption{Abstract figure displaying some relations of clone classes. Arrows represent superclass relations.}
  \label{fig:clonerelation}
\end{figure}

@@

\section{CloneRefactor}
To determine the context of clones, we use the tool CloneRefactor\footnote{CloneRefactor is a code clone detection and refactoring tool: \url{https://github.com/SimonBaars/CloneRefactor}}. CloneRefactor uses JavaParser~\cite{tomassetti2017javaparser} to parse the Abstract Syntax Tree (AST) of Java source code. We then find cloned nodes in the syntax tree, of which we map the relation, location, and contents.

CloneRefactor uses this information to propose refactorings for the detected clones. Where clone instances are located in the code has a large impact on how it can be refactored, and what the impact on the design of the code is. In that way, the categorizations that CloneRefactor proposes helps determine which clones are most suitable for refactoring, as opposed to traditional clone detection approaches that do not take clone context into account.

\section{Experimental Setup}
To find out in which location, relation and contents category most clones are found, we performed measurements on a large corpus of diverse open-source projects.
